\chapter{Everybody assumes that The Onion is satire, but you know different. Why? Because you're its main reporter, gathering news from alternate realities.}
\section{XcessiveSmash}

"Look, kid, I don't want you along, I don't want to teach you, you're an inconvenience," I said, a bit unkindly perhaps. "But I have to teach you the job, and by God I'm going to try my best to teach you the damn job."

"Are you aware that this is not Full Meta Jacket, Ms. Seraph?" Mark said with an idiotic grin. The kid was in his early twenties, tall, blond - a sharp contrast to my short stature and jet black hair - and thought, like every 20 and change kid, that he was the king of the damn world. Or worlds, as it may be. He kind of reminded me of myself actually.

Which was probably why I hated him.

"Do you know the mortality rate of our trainees, kid?" I asked, pretending I hadn't heard him.

"Wow you really think it is-"

Christ, this kid. I grabbed him by the collar and pulled him off his feet until he was inches from my face.

"75 percent. Got it?" I said, his wide blue eyes staring into the depths of my opal irises. "Three out of four die, of the remaining 25 percent, most are missing in action, stranded in some hell, and what few are left drop out. There's a reason there have been five reporters in The Onion since 1988." I let him go and kid practically fell to the floor. His eyes were wide and his face was bloodless. "Do you understand now?" I said, keeping my voice low.

The kid opened his mouth to say something then decided against it. Instead, he just swallowed and nodded. I might've overdone it a bit.

"Good," I said. "Follow my instructions and you might not die." Without waiting for a response I laid my hand across his forearm and with my other hand activated the TransTemporal-Relocator, or the TTR.

I'd been doing the job for just about two decades and I still wasn't used to the sensation. It was as if my center of gravity shifted out of my body and I stumbled as I lost my balance. But the feeling faded and we were there. Wherever that might be.

Decades of experience saved us. I'd once dropped into a a nuclear test site, and another time in the middle of a horde of demons. The first few seconds of any "Stumble" as well called it were the most dangerous.

So when I landed in the driver's seat I immediately slammed the breaks as a black coupe - what is it with black cars? - tried to ram us from the left. The car careened, when it didn't hit us and hit another car on the right. They both spun out and hit the divider in the middle of the - I looked around - twelve lane highway.

"What the fuck!?" the kid shouted next to me. Famous last words.

I briefly glanced at him - he was holding a box of pizza. We were in a sleek, red sports car. There was a GPS in front of the car and a timer in the bottom left. Five minutes, three miles away. Got it. The TTR always did this, put us in fantastical scenarios or events, and we had to play them through. Rarely longer than an hour, they were the stories I wrote for every Onion piece. It was in our best interests to play along.

“In the next one half mile, take the exit 27,” the GPS said in that infuriatingly kind voice. Some things stay constant across dimensions.

“Th-that’s impossible,” the kid said. “You’re on like the tenth lane, how’re you gonna make this exit?”

“Recklessly,” I replied. “Hold on to something.” I flung the steering wheel left and crossed two lanes immediately. A couple of people honked on their horns as I cut them off but I paid them no mind. I slammed the breaks to get behind a car on the right lane and swung left again. Four lanes to go, and the exit was in sight.

“We aren’t gonna make it,” the kid said, practically in tears. Christ, I would take overly eager over useless downer any day.

I looked in the rear view mirror and saw another one of those black cars who had tried to ram us before. In seconds he was in parallel with us to my right. I could break or speed up, forcing him to miss.

Or I could be insane.

“Sorry kid,” I said, as the car slammed into our right. I forced myself to relax though every muscle in my body screamed at me to tense up, so all I suffered was some seat-belt burn and ear damage when the car slammed into us. There was a loud bang and the screech of metal against metal. Someone screamed. I timed a sharp left as the car hit and we practically flew across the last some lanes, directly into the exit. The car tried to follow but was T-boned by a white minivan. I let out a whoop of joy as we rattled through the road.

I spared a glance at the kid. The door had dented inwards, and his arm was at an impossible angle. I checked his pulse with my hand – still alive. Small favors, I suppose.

The rest of the trip was relatively uneventful. I drove into a suburban neighborhood until the GPS indicated I’d arrived. With ten seconds left I practically ran to the doorbell and rung it, breathing heavy.

A dejected looking man in his mid-40s who reeked of vodka opened the door. “Aw, fuck you, bitch. Would it have killed you to arrive four seconds later?! Is free pizza really that much of a fucking loss?”

Lovely.

I pointed to dented my car and the dying intern. “Yeah, you douche-bag, it is.”

The TTR beeped, the end of the experience. The device was really completely outside our control. It chose the location, the experience, and when it ended. Once more I “Stumbled,” and we were back in my office. I didn’t have to be in contact with the kid on the return trip, and so he was there to as we were thrown roughly back into our own reality. The poor kid let out a strangled scream as he landed on top of his broken arm.

The medics were already on standby and rushed to help the kid. I watched as they put him on a stretcher and escorted him out. I shook my head. Idiot. Should never have signed up for this.

I sighed and went over to my computer to start the article. “Pizza Corporatism: The lengths pizza Companies will go to make sure you don’t get free pizza.”

%---------------------------%

\chapter{After dieing of old age, you wake up to realize you just slept for 2 days and dreamed an entire life. You now have the wisdom of an elderly person but the body of a 20 something.}
\section{thattaekwondogirl}

There's a joke they always tell. If a woman dies, her husband will die within a year. If a man dies, his wife will go on a cruise.

Well, there was some truth to it. I had gone on a cruise. My nieces and nephews - I'd never had children - had convinced me to. It was nice, but I was haunted by that aching loss. It had served only as a distraction. Nothing had been the same since he passed. Every day felt empty. Before, I would wake up every morning, sunlight streaming into our cheerful blue room, and see him next to me, a smile on his face. "You look so peaceful when you sleep," he always told me. And then he would kiss me on the head, and everything was right with the world.

Now I woke up to an untouched pillow. Nobody ever talks about how cold the bed gets after spending a lifetime sharing it with someone else.

But now... Now I was starting to feel warm again. I was dying. I knew that much. I didn't know if I believed in an afterlife, but I hoped I'd get to meet him again.

I turned, my aged face cracking a smile at my youngest niece. Even she was already in her 30's. I was so tired, and yet I mustered up just a little more energy, patting her hand gently with my own frail one. I'd helped to raise her when my sister was fighting her own demons. When my sister was institutionalized, my niece had come to live with me for months until her mother was better. Explaining mental illness to an 11-year old was difficult. Old enough to understand that something was wrong, yet still too young to fully grasp the situation. But I was grateful. I loved my sister, and would do anything to help her. The fact that I had become so close to her daughter was just an added bonus. My niece's tear-stricken face managed a smile back.

"Don't cry," I said softly. I wished I could wipe the tears from her face, just like I'd done when she was younger. "I had a good life." As if I had been holding on just long enough to say that, I felt the rest of my energy leave me. I smiled wordlessly, my eyes drifting closed, the green walls fading away as I felt myself relaxing into the warm embrace of death. I had had a good life. I was at peace.

And then... My eyes opened. Maybe I hadn't died at all. I looked around, but my niece was nowhere to be found. The ache was gone from my body. I looked down at my hands, no longer spotted with age. Hm. Was this the afterlife?

I took my surroundings in carefully. I noted in the back of my mind that I was drenched in sweat. Blue walls. Blue walls. I'd died in a room painted green. But the blue...

Hopefully, I turned to my left, my heart fluttering in my chest. But... Nothing. An empty pillow besides me, perfectly fluffed, indicating that there hadn't been a head resting on it all night. I felt tears welling in my eyes. Was this hell? Was I doomed to spend eternity like this, never being able to see him ever again? What had I done wrong?

I reached hesitantly toward the pillow, expecting some monster to jump at me, but my hand made it safely to the soft pillow. Slowly, I pulled it toward me, and as I did, I caught a whiff of something I hadn't smelled in years. My husband.

The tears were coming quickly now, and I buried my face in the pillow, sobbing. It was undoubtedly his scent. I wasn't sure whether I was comforted or tormented by that thought. If this was hell, I'd at least enjoy this while it lasted. I'd been devastated when I realized his smell had faded from my home after his death. It had been the last lingering, tangible memory of him. Without it, the warmth had truly gone from my bed. But I was warm again. Here in this moment, I was warm.

I cried, clutching the pillow as if it could be ripped away from me at any moment. For all I knew, it could be.

"Babe?"

I froze. No. It couldn't be. My face stayed in the now soaked pillow.

I heard something get set down on a surface, then footsteps approaching me across the carpeted room. I didn't turn, fearing that I'd see some demon with his voice. The footsteps stopped, and I could sense someone behind me. I felt a warm, reassuring hand on my shoulder.

"Oh, honey, you're awake!" His voice broke, and I could hear the concern and relief all rolled up into one in it. The hand gently pulled my shoulder to turn me around.

I blinked, my vision still blurred with tears. Dark hair, tan skin. I blinked some more. The moment of clarity was instantly gone as recognition set in. I started bawling, overwhelmed by emotion. It was him. It was really him. I was safe.

"What's wrong? Why are you crying? Oh- babe- what-" He was cut short as I lunged forward, hugging him tightly.

"I missed you. I missed you so much - you don't know how much it hurt," I manage to choke out through the tears.

His warm chuckle was music to my ears. "What do you mean, missed me?"

"You died, asshole! I never gave you permission to die first! You- there was nobody for me to cuddle with- you were- oh god, I love you so much," I said.

I felt his hands gently pull me away from him, concern on his face. One of his hands rested gently on my forehead, while the other tilted my chin up to look at him. "What are you talking about? You've been asleep for the past two days. I was so scared - you had a fever and were coughing like crazy. The doctor told me to wait it out though - you haven't been sleeping enough recently, honey."

My brow furrowed in confusion. Asleep? Two days? But... I'd lived an entire lifetime. I'd just died, for crying out loud. Was he trying to tell me all of that was just some fever-induced, hyper-realistic dream? "But... It felt so real," I replied. "How would you know we're not both dead?"

He chuckled, clambering over me to settle in bed beside me. The bed shifted and creaked in a way I hadn't realized I'd missed. He reached out, combing his fingers through my damp hair thoughtfully. I then remembered that I'd woken up drenched in sweat.

"Getting all philosophical on me already?" he teased, giving a strand of my hair a playful tug. "Even if we are, why does it matter right now? I'm happy right now." His strong arms wrapped around me, pulling me close. "This could be life, or it could be heaven, but all I know is that I have you, and you're safe, and that's all that matters."

As I relaxed into his arms, I knew it was true. I was sure there was some way to find out whether I was alive or not, but for now, all I needed was him. The love of my life. Nothing else mattered right then. I felt him kiss me on the head, and I knew that everything was right in the world.

\chapter{Suddenly the whole world hears a voice from the sky: Hi guys, God here. I'm being promoted to the Andromeda galaxy and I'm here to introduce my replacement, Bob this is earth, earth this is Bob. Have fun, pleasure to meet you all!!}
\section{thewanderingway}
Everyone stopped what they were doing and turned their heads up to the sky. Had they heard correctly, God was leaving and left some man named Bob in charge? People in the cities looked out their windows, and stepped out of their cars looking upward for more answers. Meanwhile, in the Vatican, Pope Francis and his cardinals were discussing what implications this news might mean. Elsewhere still, the Grand Seer of the Church of the Apocalyptic Holy Trinity, looked upon his flock and reasoned, now would be a good as any time to bring out the Kool-aid.

As the people of the world waited for news from this Bob, many began to fear and question all of reality. As Joshua McCabe picked up a brick in rage, as Nikolai Kaparov was stepping off the ledge of his building in fear, and as Pablo Gutierrez reached for the bottle of booze that would drown him, a gentle caring voice boomed from the heavens.

"Hello I'm Bob Ross. I'm grateful to be welcomed into all your lives. This is a first for me, but I want to thank you all for allowing me the opportunity to be God's replacement. I never imagined this would happen, but there are no mistakes, just happy accidents."

And thus the world was good, and calmed. The sky turned a brilliant shade of Phallo Blue with clouds of Titanium White.